---
title: "FurtherOptimizationSci"
author: "xiucheng quek"
date: "22 June 2016"
output: word_document
---


Read in tables, there are 3 tables. `ranked.tsv` contains the cumulative score of the top parameters. `combination.index.txt` contains the table that maps the combination the the combination_id in `ranked.tsv`. `seq.index.txt` containst the index for the sequence pair


```{r}
rankTable <- read.table('ranked.tsv', sep='\t', header=TRUE)
comb <- read.table('combination.index.txt', sep='\t', header=TRUE)
seq_pair <- read.table('seq.index.txt', sep='\t', header=TRUE)
```


## Get the top 10 sci score


```{r}

mergedTable <- merge(rankTable, comb, by.x='combination', by.y='index')
mergedTable <- mergedTable[order(mergedTable$score),]
write.table(head(mergedTable, n = 100) , file='top100.tsv', sep ='\t', quote = F, col.names =F, row.names = F)

```

## Factor Analysis to Confirm findgs

Based on the rank score above, it appears that varying T and S has no impact on the SCI score. t of 0.4 should be used instesad

To confirm our findings, I did a factor analysis using anova


```{r}
# First read in table containing sci score
sci_scores <- read.table('merged_sci_diff.txt', sep='\t', header=TRUE)
# factorize 
as.factor(sci_scores$sequence) -> sci_scores$sequence
as.factor(sci_scores$combination) -> sci_scores$combination
## merged data



merged_scores <- merge(sci_scores, comb, by.x='combination', by.y ='index')
```

Due to the large number of combination of factors, I did one way anova for first without testing for factors independence. They will be corrected using tukey honestly significant difference test for multiple comparisions for each factors


# One way anova 

Appears only that variance f T values score are different.
```{r}
taov<-aov(sci.diff ~ as.factor(t) + as.factor(S) + as.factor(T) + as.factor(k), data = merged_scores)
TukeyHSD(taov)
```
## Lets make sure that we are not violating assumptions of annova test 






Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
